---
title: "Lab 02 - Plastic waste"
author: "Bob Dwyer"
date: "Sys. Date()"
output: html_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1
#### The largest plastic waste per capital belongs to Tinidad & Tobago (N.America). Forbes states that "Inadequate waste management is at the root of the problem."

```{r plastic-waste-continent}
plastic_waste %>% 
  ggplot(aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = .1) +
  facet_wrap(~ continent)
```

### Exercise 2
#### Describe why we defined the color and fill of the curves by mapping aesthetics of the plot but we defined the alpha level as a characteristic of the plotting geom.
##### Answer: Color and fill are assigned to specific variables, whereas, adding the alpha aesthetic to a geom assigned the aesthetic universally, and can almost be thought of as a graph setting.

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.25)
```

### Exercise 3
#### What features are apparent in the box plots but not in the violin plots?
##### Answer: A violin plot in addition to showing distribution / summary statistics, visually, it also shows density.

```{r plastic-waste-violin}
plastic_waste %>% 
  ggplot(aes(x = continent, y = plastic_waste_per_cap)) +
  geom_violin()
```

### Exercise 4
#### Visualize the relationship between plastic waste per capita and mismanaged plastic waste per capita using a scatterplot. Describe the relationship.
##### There is a direct, postive relationship.

#### Does there seem to be any clear distinctions between continents with respect to how plastic waste per capita and mismanaged plastic waste per capita are associated?
##### The story is that as plastic_waste_per_cap increases, so does the amount of mismangaged plastic waste. However, we do see that on some continents, the amount of mismangaged waste increases at a slower rate (e.g., North America, Europe) 

```{r plastic-waste-mismanaged}
plastic_waste %>% 
  ggplot(aes(x = plastic_waste_per_cap, 
             y = mismanaged_plastic_waste_per_cap, color = continent)) +
  geom_point(size = 2)
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged_}
# This figure is above. There is a mis-match between the code and the assignement on the website.
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# This figure is above. There is a mis-match between the code and the assignement on the website.
```

### Exercise 7

#### There does not seem to be a strong linear relationship here.

```{r plastic-waste-population-total}
plastic_waste %>% 
  ggplot(aes(x = total_pop, 
             y = plastic_waste_per_cap, color = continent)) +
  geom_point(size = 2)
```

```{r plastic-waste-population-coastal}
plastic_waste %>% 
  ggplot(aes(x = coastal_pop, 
             y = plastic_waste_per_cap, color = continent)) +
  geom_point(size = 2)
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
plastic_waste %>% 
  mutate(coast_pop_prop = coastal_pop / total_pop) %>% 
  filter(plastic_waste_per_cap < 1.0) %>% 
  ggplot(aes(x = coast_pop_prop, 
             y = plastic_waste_per_cap)) +
  geom_point(aes(color = continent)) + 
  geom_smooth(color = "black") +
  labs(title = "Plastic Waste vs. Coastal Population Proportion",
       subtitle = "by continent",
       x = "Coastal Population Proportion (Coastal / Total Population)",
       y = "Plastic Waste Per Capita",
       color = "Continent")
```

## Pro-Tips

### Excercise 3

Try this :D
``` {r try this code}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```  

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements